\documentclass[a4paper,10pt]{article}
\usepackage{moderncv}
\moderncvstyle{classic} % Choose style: classic, casual, banking, oldstyle, fancy
\moderncvcolor{blue} % Color theme: blue, orange, green, red, purple, grey, black
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry} % Reduce the scale to fit more on one page

% Personal information
\name{Md Tousif Hasan}{Lavlu}
\title{Lecturer | Researcher | Software Developer}
\address{Dhaka, Bangladesh}{}
\phone[mobile]{+880 XXXXXXXXXX} % Replace with actual number
\email{email@example.com} % Replace with actual email
\social[github]{github.com/tousif-lavlu} % Replace with actual GitHub profile
\social[linkedin]{linkedin.com/in/tousif-lavlu} % Replace with actual LinkedIn profile

\begin{document}
\makecvtitle

\section{About Me}
Hello, this is Md Tousif Hasan Lavlu. Currently, I am serving as a Lecturer at Shanto-Mariam University of Creative Technology, Department of CSE. I completed my Bachelor of Science in Computer Science and Engineering from BRAC University and am currently pursuing a Master of Science in Information and Communication Technology at Bangladesh University of Engineering and Technology (BUET). I have a strong interest in Machine Learning, particularly in its application to solve complex problems across various domains. My research focuses on enhancing machine learning models' predictive capabilities through novel techniques, including reinforcement learning for adaptive systems, federated learning for privacy-preserving collaboration, computer vision for improved visual interpretation, and cognitive computing to simulate human thought in complex scenarios.

\section{Interests}
\cvitem{}{Machine Learning}
\cvitem{}{Computer Vision}
\cvitem{}{Federated Learning}
\cvitem{}{Reinforcement Learning}
\cvitem{}{Cognitive Computing}
\cvitem{}{Health Informatics}

\section{Experience}
\cventry{November 2022 -- Present}{Lecturer}{Shanto-Mariam University of Creative Technology}{Dhaka, Bangladesh}{}{
\begin{itemize}
    \item Actively mentor students participating in competitive programming, guiding them through problem-solving techniques, algorithmic thinking, and contest preparation.
    \item Serve as a problem setter and moderator for various competitive programming contests, enabling students to experience real-world problem-solving scenarios.
    \item Mentor students in conducting research on machine learning, guiding them from research formulation to achieving results. Supervised projects in Python, Java, C++, and more.
\end{itemize}}

\section{Education}
\cventry{July 2023 -- Present}{MSc in Information and Communication Technology}{Bangladesh University of Engineering and Technology (BUET)}{Dhaka, Bangladesh}{}{
\begin{itemize}
    \item Researching machine learning applications to enhance healthcare services, focusing on predictive modeling and data standardization.
    \item Completed a term paper on hyperparameter tuning using the United States Congressional Voting Records dataset from UCI.
    \item Wrote a review paper titled “Key Algorithms in Chatbot Development: A Comprehensive Review.”
    \item Developed embedded systems titled Adjustable Digital Clock using STM32 microcontrollers.
\end{itemize}}

\cventry{May 2018 -- May 2022}{BSc in Computer Science and Engineering}{BRAC University}{Dhaka, Bangladesh}{}{
\begin{itemize}
    \item Thesis: Machine Learning Based Career Suggestive System in the Informal Job Sector Considering Cognitive Skills.
    \item Achieved above 90\% marks in key courses including Data Structure, Algorithm, Artificial Intelligence, Neural Networks, and Robotics.
    \item Actively participated in programming contests, enhancing my problem-solving skills and algorithmic thinking.
    \item Held leadership roles in clubs, organizing seminars, events, and hackathons.
\end{itemize}}

\section{Projects}
\cvitem{Adjustable Digital Clock using STM32 Microcontroller}{Developed an adjustable digital clock system using STM32 microcontroller for time management applications.}
\cvitem{Online Car Shop}{Worked on an e-commerce project for an online car shop with full-stack features.}
\cvitem{Online Technician Service}{Developed a service platform to connect technicians with customers for home repair services.}
\cvitem{Pytorch Project}{Explored PyTorch for implementing neural network models in various machine learning tasks.}
\cvitem{Research CV Template}{Created a researcher website-CV using Hugo, GitHub Pages, and moderncv-LaTeX template.}
\cvitem{Term Paper on Hyperparameter Tuning}{Completed term paper on hyperparameter tuning in machine learning algorithms using UCI datasets.}

\end{document}
